How residence time constrains diversity

### 2015-06-01 analyses/ResTime.Rmd

```{r, results = 'hide'}
rm(list=ls()) 
getwd() 
setwd("~/GitHub/QuantitativeBiodiversity/Assignments/Alpha") 
```

@@

```{r}
sim.data <- read.csv("~/GitHub/hydrobide/results/simulated_data/SimData.csv")  
```

>>>>

```{r, results = 'hide'}
rm(list=ls()) 
getwd() 
setwd("~/GitHub/hydrobide") 
```

@@

```{r}
sim.data <- read.csv("./results/simulated_data/SimData.csv")  
```
